HCI Draft Paper

### 2015-11-30 sigchi-latex-proceedings 2/draft-paper.tex
experimental design

\section{Experimental Design}

>>>>

\section{Experimental Design}
The experiment had a one-way within-subject design with the multitasking interface (stacked and non-stacked) acting as a two-level independent variable. Order effects were counterbalanced by switching the order of testing with two groups of participants. The first group tested the stacked interface first, while the second group tested the non-stacked interface first. Time to completion and accuracy served as the dependent variables. Participants performed the set of tasks twice for each stacked and non-stacked multitasking interfaces with two different experimenters.

Randomizing participants into groups allowed us to minimize the variance any participants may have had in terms of greater experience or comfort with one interface over the other. Since the experimental tasks are repetitive, we were susceptible to the learning-effect. However, counterbalancing based on the two levels of the independent variable allowed us to account for it.

We designed the tasks to cover the three most common interactions with the multitasking interface. Firstly, minimal, where the participant’s interaction with the multitasking interface is limited to one or two switches. Secondly, a longer but a real world representative task where the participant switches between three or more apps. Lastly, repetitive switching, a common scenario where the participant repeatedly switches between two apps to achieve a specified goal. Combined with a within-subject design where the participant performs these tasks multiple times on each level gave us a very comprehensive set of data points to test our hypothesis.
